---
title: "Alcohol vs Seat choice"
author: "Eileen Dunn"  
date: "Summer 2024"  
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

## Introduction
Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??  

The data came from UCDavic in the year...

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.  

$H_A$: The average number drinks is different between at least two rows.   

# Methods:

In the data set davisdata Seat is a categorical variable, alcohol is numerical.

We try to predict alcohol ~ Seat so we use the num~cat helper file.  

## Results


### Descriptive Results


### Graphical summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

Now add a boxplot

```{r}
basicCN + geom_boxplot()
```

This boxplot shows that the back seat has the most variation in alcohol levels, while the front seat has the least.  

### Numerical summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The numerical summary shows
In the back seat, alcohol levels range from 0 to 55, with a typical value around 3.5 and an average of 8.56  
In the fron seat, alcohol levels range from 0 to 35, with a typical value around 1 and an average of 3.33  


### Inferential Results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is 0.000116, less than 0.05 so we reject the null hypothesis.  
There is a difference in alcohol consumption based on where people sit.  


```{r}
plot(TukeyHSD(model1))
```

This shows that the middle-bakc consume more alcohol than middle-front.  

## Conclusions

The seats in the back have a higher average of people consuming alcohol than those in the front or middle seats. The Tukey plot shows that the chances of the seat positions have a low probability of the alcohol levels between the different seat positions.  
The seats in the back have a higher average of people consuming alcohol than those in the front of middle seats. Since the p-value is 0.000116, less than 0.005 so we reject the null hypothesis.
The tukey plot shows that there is a difference in alcohol consumption based on where people sit.
